Code to reproduce results in _Semi-parametric generalized linear model for

### 2021-12-23 ManuscriptCode/Manuscript.Rmd
Prettify manuscript plots

set.seed(20210814)
data(boric_acid)
```

@@

We will have one binary predictor $X_1 \sim Bern(0.5)$ with $beta_1=0.5$ and one continuous predictor $X_2 \sim N(0,1)$ with $\beta_2 = 1$. The cluster size distribution will be binomial.

@@

  cs <- rbinom(n, size=maxClusterSize, prob=aveClusterSize/maxClusterSize)

@@

```{r Compare}
comb <- bind_rows(`Both correct` = sim1, 
                  `BB correct`= sim2,
                  `SPGLM correct` = sim3, 
                  `Neither correct` = sim4,
                  .id="Generator")

# get correct values of parameters 
correct_beta <- tibble(Term = c("(Intercept)","X1","X2"),
                  Correct = beta_correct)
correct_pdf <- bind_rows(`Both correct` = pdf1, 
                         `BB correct`= pdf2,
                         `SPGLM correct` = pdf3, 
                         `Neither correct` = pdf4,
                         .id="Generator") %>%
  mutate(Term = as.character(NResp))

@@

```{r ComparePlot}
ggplot(comb_beta, aes(x=Term, y=Est-Correct, colour=Model, shape=Model)) +
  facet_wrap(~Generator) +
  geom_hline(aes(yintercept=0)) +
  stat_summary(fun.data =  mean_sdl, geom="pointrange", position=position_dodge(width=0.4))

@@

```{r PDFplot}
ggplot(comb_pdf, aes(x=NResp, y=Est, colour=Model)) +
  facet_wrap(~Generator) +
  geom_line(aes(y=Correct), col="black") +
  stat_summary(fun.data =  mean_sdl, geom="pointrange", position=position_dodge(width=0.1))

>>>>

set.seed(20211223)
data(boric_acid)
```

@@

We will have one binary predictor $X_1 \sim Bern(0.5)$ with $\beta_1=0.5$ and one continuous predictor $X_2 \sim N(0,1)$ with $\beta_2 = 1$. The cluster size distribution will be binomial.

@@

  cs <- rbinom(n, size=maxClusterSize, prob=aveClusterSize/maxClusterSize)
  cs <- pmax(1, cs) # don't want clusters of size 0

@@

```{r Compare}
comb <- bind_rows(`Both correct` = sim1, 
                  `BB correct`= sim2,
                  `SPGLM correct` = sim3, 
                  `Neither correct` = sim4,
                  .id="Generator") %>%
  mutate(Generator= factor(Generator, levels = c("Both correct",
                                                 "BB correct",
                                                 "SPGLM correct",
                                                 "Neither correct")),
         Model = factor(Model, levels = c("BB","SPGLM","GEE")))

# get correct values of parameters 
correct_beta <- tibble(Term = c("(Intercept)","X1","X2"),
                  Correct = beta_correct)
correct_pdf <- bind_rows(`Both correct` = pdf1, 
                         `BB correct`= pdf2,
                         `SPGLM correct` = pdf3, 
                         `Neither correct` = pdf4,
                         .id="Generator") %>%
  mutate(Term = as.character(NResp),
         Generator= factor(Generator, levels = c("Both correct",
                                                 "BB correct",
                                                 "SPGLM correct",
                                                 "Neither correct")))

@@

```{r ComparePlot}
cols <- RColorBrewer::brewer.pal(3, "Set2")
names(cols) <- levels(comb$Model)
ggplot(comb_beta, aes(x=Term, y=Est-Correct, fill=Model, outlier.fill=Model)) +
  facet_wrap(~Generator) +
  geom_hline(aes(yintercept=0)) +
  geom_boxplot(position=position_dodge(width=0.4), width=0.3, 
               outlier.size =1, outlier.alpha=0.5) +
  scale_y_continuous("Bias = Estimate - correct value") +
  scale_fill_manual(breaks=names(cols), values=cols)

@@

```{r PDFplot}
ggplot(comb_pdf, aes(x=NResp, y=Est, fill=Model, outlier.fill=Model)) +
  facet_wrap(~Generator) +
  geom_line(aes(y=Correct), colour="black", size=1) +
  geom_boxplot(aes(group=interaction(Model, NResp)), 
               position=position_dodge(width=0.6), width=0.5, 
               outlier.size =1, outlier.alpha=0.5) +
  scale_y_continuous("Probability") +
  scale_x_continuous("# of responses", breaks = 0:cs_predict) +
  scale_fill_manual(breaks=names(cols), values=cols)
